---
title: "Multiple Linear Regression"
author: "Author : Rose Ellison"
output:
  html_document:
    highlight: tango
    number_sections: no
    number_subsections: no
    theme: paper
    smooth_scroll: true
  pdf_document:
    highlight: tango
    number_sections: no
    number_subsections: no
    theme: paper
    smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(caTools)
library(ggplot2)
```

I will be building a multiple linear regression model based off the '50_Startups' data and using the forward elimination model. 
In this dataset there are five columns $Profit$, $R.D.Spend$, $Administration$, $Marketing$, and $State$. Profit is our dependent variable while the other four are our independent variables. 
We want to determine if there are any correlations between the profit and expenditures, such as r&d, admin, and marketing. Additionally, is there any correlation between profit and which state the company is operating?


\[Multiple Linear Regression Formula : \]

\[y = b_0 + b_1  x_1 +  b_2  x_2 + b_3  x_3 +  b_4  x_4\]

## Preparing the data
For this step, I need to read in the csv file, deal with categorical data, and then split the data into training and test sets. 
```{r}
# Importing the dataset
startups <- read.csv('../data/50_Startups.csv')


# Dealing with categorical data - 'State'
# Encoding
startups$State <- factor(startups$State,
                         levels <- c('New York', 'California', 'Florida'),
                         labels <- c(1, 2, 3))


# Splitting the data into test and training sets
set.seed(1)
split <- sample.split(startups$Profit, SplitRatio = .8)
training.set <- subset(startups, split == TRUE)
test.set <- subset(startups, split == FALSE)
```





## Fitting Multiple Linear Regression to the Training Set
The Independent variable, Profit, is going to be a linear combination of all the dependent variables.
```{r}
# Regressor with all dependent variables
regressor <-  lm(Profit ~ ., training.set)
summary(regressor)
```

According to the data, the only strong predictor in profit is the r&d spend. Due to this, we could rewrite our regressor with only one dependent variable and we should still get the same results.

```{r}
# Regressor with only the R.D.Spend dependent variable
regressor <-  lm(Profit ~ R.D.Spend, training.set)
summary(regressor)
```
Although we changed the regressor to only using the R.D.Spend variable, the p-value remains the same. This is another indication that R.D.Spend is the only strong dependent variable predictor. 


## Predicting the Test Set Results
```{r}
y.pred <- predict(regressor, newdata = test.set)
```

## Visualizing the training set
```{r}
# Visualizing the training set results
ggplot() + 
  geom_point(aes(x = training.set$R.D.Spend, y = training.set$Profit), col = 'lightblue', lw = 4) + 
  geom_line(aes(x = training.set$R.D.Spend, y = predict(regressor, newdata = training.set)), col = 'darkblue') + 
  theme_bw() + 
  ggtitle('Profit VS R.D.Spend (Training Set)') + 
  xlab('Research and Development Spend') + 
  ylab('Profit')
```

## Visualizing the test set results
```{r}
ggplot() + 
  geom_point(aes(x = test.set$R.D.Spend, y = test.set$Profit), col = 'lightblue', lw = 4) + 
  geom_line(aes(x = training.set$R.D.Spend, y = predict(regressor, newdata = training.set)), col = 'darkblue') + 
  theme_bw() + 
  ggtitle('Profit VS R.D.Spend (Test Set)') + 
  xlab('Research and Development Spend') + 
  ylab('Profit')
```
